Рекурсивные свойства ветвления и БГГ резольвента

### 2011-02-11 AffineLieAlgebras/MQFT2010/article-ru.tex
More work on translation

\begin{remark}
This relation can be considered as a generalized form of the Weyl formula
for the singular element $\Psi _{\frak{g}}^{\mu }$: the vectors $\mu _{%
\widetilde{\mathfrak{a}}}\left( u\right) $ play the role of singular weights
while the alternating factors $\epsilon (u)$ are extended to $\epsilon
(u)\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$. In
fact when $\frak{a=g}$ both $\frak{a}_{\perp }$and $\frak{h}_{\perp }$are
zeros, $U=W$, and\ the original Weyl formula is reobtained so far as the singular elements $\epsilon (u)\Psi _{\frak{a}_{\perp
}}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\epsilon (u)$ become trivial.
 In the opposite
limit when $\frak{a=0}$, $\Delta _{\frak{a}_{\perp }}=\Delta _{\frak{g}}$, $%
\frak{h}_{\perp }^{\ast }=0$, $\frak{a}_{\perp }=\frak{g}$, $\mathcal{D}_{%
\frak{a}_{\perp }}=0$ and $U=W/W_{\frak{a}_{\perp }}=e$ the singular element
 $\Psi ^{\mu }$ is again reobtained, now via the trivilization of the set of
 vectors $\mu _{\af}\left( e\right) =0$.
\end{remark}

@@

In \cite
{2010arXiv1007.0318L} the decomposition analogous to (\ref{singular main}) was
used to construct the recurrent relations for branching coefficients $k_{\xi
}^{\left( \mu \right) }$ corresponding to the injection $\frak{a}%
\hookrightarrow \frak{g}$:
\begin{equation}
\begin{array}{c}
k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
\widetilde{\frak{a}}}(u(\mu +\rho )-\rho )}+\right.  \\
\left. +\sum_{\gamma \in \Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}%
}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right)
}\right) .
\end{array}
\label{recurrent rel}
\end{equation}
The recursion is goverened by the set $\Gamma _{\widetilde{\frak{a}}%
\rightarrow \frak{g}}$ called the injection fan. The latter is defined by the
carrier set $\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}$ for the
coefficient function $s(\xi )$
\begin{equation*}
\left\{ \xi \right\} _{\widetilde{\frak{a}}\rightarrow \frak{g}}:=\left\{
\xi \in P_{\widetilde{\frak{a}}}|s(\xi )\neq 0\right\}
\end{equation*}
appearing in the expansion
\begin{equation}
\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
_{\widetilde{\frak{a}}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}%
_{\frak{a}}(\pi _{\widetilde{\frak{a}}}\alpha )}=-\sum_{\gamma \in P_{%
\widetilde{\frak{a}}}}s(\gamma )e^{-\gamma };\quad
\end{equation}
The weights in $\left\{ \xi \right\} _{\widetilde{\frak{a}}\rightarrow \frak{%
g}}$ are to be shifted by $\gamma _{0}$ -- the lowest vector in $\left\{ \xi
\right\} $ -- and the zero element is to be eliminated:
\begin{equation}
\Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}}=\left\{ \xi -\gamma
_{0}|\xi \in \left\{ \xi \right\} \right\} \setminus \left\{ 0\right\} .
\end{equation}

The recursion relation (\ref{recurrent rel}) was originally used to
describe branchings for integrable modules. Notice that there exists an
important class of modules that also can be reduced with the help of the
injection fan --
these are Verma modules.
\end{remark}

\subsection{Weyl-Verma formulas.}

>>>>

\begin{remark}
Это соотношение можно рассматривать как обобщенную форму формулы Вейля для сингулярного элемента $\Psi _{\frak{g}}^{\mu }$: векторы $\mu _{%
\widetilde{\mathfrak{a}}}\left( u\right) $ играют роль сингулярных весов, а чередующиеся множители  $\epsilon (u)$ расширены до $\epsilon
(u)\Psi _{\frak{a}_{\perp }}^{\mu _{\frak{a}_{\perp }}\left( u\right) }$.

Действительно, при  $\frak{a=g}$ подалгебры  $\frak{a}_{\perp }$, и $\frak{h}_{\perp }$ тривиальны, $U=W$ и оригинальная формула Вейля восстанавливается, так как сингулярные элементы $\epsilon (u)\Psi _{\frak{a}_{\perp %
}}^{\mu _{\frak{a}_{\perp }}\left( u\right) }=\epsilon (u)$ становятся  тривиальными.

В противоположном пределе, когда $\frak{a}=0$, $\Delta _{\frak{a}_{\perp }}=\Delta _{\frak{g}}$, $%
\frak{h}_{\perp }^{\ast }=0$, $\frak{a}_{\perp }=\frak{g}$, $\mathcal{D}_{%
\frak{a}_{\perp }}=0$ и $U=W/W_{\frak{a}_{\perp }}=e$, опять восстанавливается сингулярный элемент
 $\Psi ^{\mu }$, теперь в результате тривиализации множества векторов $\mu _{\af}\left( e\right) =0$.
\end{remark}

@@

В работе \cite{2010arXiv1007.0318L} разложение, аналогичное формуле (\ref{singular main}) было использовано для построения рекуррентных соотношений для коэффициентов ветвления $k_{\xi}^{\left( \mu \right) }$, соответствующих вложению  $\frak{a}\hookrightarrow \frak{g}$:
\begin{equation}
\begin{array}{c}
k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
\widetilde{\frak{a}}}(u(\mu +\rho )-\rho )}+\right.  \\
\left. +\sum_{\gamma \in \Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}%
}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right)
}\right) .
\end{array}
\label{recurrent rel}
\end{equation}
Рекурсия задается множеством  $\Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}}$, называемом веером вложения. Это множество определяется как носитель  $\left\{ \xi \right\}_{\frak{a}\rightarrow \frak{g}}$  коэффициентной функции $s(\xi )$
\begin{equation*}
\left\{ \xi \right\} _{\widetilde{\frak{a}}\rightarrow \frak{g}}:=\left\{
\xi \in P_{\widetilde{\frak{a}}}|s(\xi )\neq 0\right\},
\end{equation*}
возникающей в разложении 
\begin{equation}
\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
_{\widetilde{\frak{a}}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}%
_{\frak{a}}(\pi _{\widetilde{\frak{a}}}\alpha )}=-\sum_{\gamma \in P_{%
\widetilde{\frak{a}}}}s(\gamma )e^{-\gamma };\quad
\end{equation}
Веса из множества $\left\{ \xi \right\} _{\widetilde{\frak{a}}\rightarrow \frak{%
g}}$ сдвигаются на $\gamma _{0}$ -- младший вектор в $\left\{ \xi
\right\} $ -- и исключается нулевой элемент:
\begin{equation}
\Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}}=\left\{ \xi -\gamma
_{0}|\xi \in \left\{ \xi \right\} \right\} \setminus \left\{ 0\right\} .
\end{equation}

Рекуррентное соотношение (\ref{recurrent rel}) первоначально использовалось для описания ветвления интегрируемых модулей. Заметим, что существует важный класс модулей, которые также могут быть редуцированы при помощи веера вложения -- это модули Верма.
\end{remark}

\subsection{Фомулы Вейля-Верма.}
